### 2013-06-14 analytical_approximation/analytic.tex
stuff'

\documentclass{article}
\usepackage{amsmath, url, geometry}
\begin{document}

@@

$$
p_Q(q) = \frac{\lambda}{2^{N/2} \Gamma(\frac{N}{2})} \int_{-\infty}^\infty |y| e^{-\lambda qy} y^{N/2-1}e^{-y/2}dy
$$

$$
p_Q(q) = \frac{\lambda}{2^{N/2} \Gamma(\frac{N}{2})} \int_{-\infty}^\infty |y|  y^{N/2-1}e^{-(\lambda q + 1/2) y}dy
$$

@@

$$
p_Q(q) = \frac{\lambda}{2^{N/2} \Gamma(\frac{N}{2})} \left(\lambda q + \frac{1}{2}\right)^{-\frac{N}{2} - 1} \Gamma(N/2+1)
$$

$$
p_Q(q) = \frac{N\lambda}{2^{\frac{N}{2} + 1}} \left(\lambda q + \frac{1}{2}\right)^{-\frac{N}{2} - 1} 
$$

>>>>

\documentclass{article}
\usepackage{amsmath, url, geometry, graphicx}
\begin{document}

@@

$$
p_Q(q) = \frac{1}{2^{N/2} \Gamma(\frac{N}{2})} \int_{-\infty}^\infty |y| e^{-qy} y^{N/2-1}e^{-y/2}dy
$$

$$
p_Q(q) = \frac{1}{2^{N/2} \Gamma(\frac{N}{2})} \int_{-\infty}^\infty |y|  y^{N/2-1}e^{-(q + 1/2) y}dy
$$

@@

$$
p_Q(q) = \frac{1}{2^{N/2} \Gamma(\frac{N}{2})} \left(q + \frac{1}{2}\right)^{-\frac{N}{2} - 1} \Gamma(N/2+1)
$$

$$
p_Q(q) = \frac{N}{2^{\frac{N}{2} + 1}} \left(q + \frac{1}{2}\right)^{-\frac{N}{2} - 1} 
$$

Since $R(q)$ is invertible, we get (?)

$$
p(r) = \frac{N}{2^{\frac{N}{2} + 1}} \left(\frac{1}{r^2} - \frac{1}{2} \right)^{-\frac{N}{2} - 1}
$$

Next step: What if it's \emph{not} a unit-ball? If the ball of of radius $R$, then that just sets the unit system, so  we have something like: (need a new normalization condition?)

$$
p(\frac{r}{R}) \propto \frac{N}{2^{\frac{N}{2} + 1}} \left(\frac{R^2}{r^2} - \frac{1}{2} \right)^{-\frac{N}{2} - 1}
$$

So how do we go from here to the quantity we want, which is $p(r|R)$?

\begin{figure}[h]
\centering
\includegraphics[width=3in]{p_of_r.png}
\caption{The $p(r)$ expression looks reasonable. In higher dimensions, the distribution is more peaked towards the surface at $r \approx 1$. But I think the normalization is off}
\end{figure}

We're going to have a lot of observations of $r$. If we assume that they're independent, then our log likelihood is

$$
\mathcal{L} = -\left( \frac{N}{2} - 1\right) \sum_i \log \left( \frac{R^2}{r_i^2} - \frac{1}{2} \right)
$$

Taking the derivative of the log likelihood with respect to $R$, we have
$$
\frac{\partial \mathcal{L}}{\partial R} = - \sum_i \frac{4R}{r_i^2 - 2R^2} = 0
$$

How do I solve this for $R$?
